%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Gulfstream Aerospace Corporation} % Organization
    {Savannah, Georgia, USA} % Location
    {Jan. 2020 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead sales forecasting efforts, achieving 90\%+ accuracy for quarter over quarter forecasts.}
        \item {Managed a data transport project that ingested over 100GB/mo. of sensor data to long term storage for future machine learning projects.}
        \item {Performed exploratory machine learning projects to evaluate efficacy of predictive maintenance business models.}
        \item {Developed dashboards in Power BI that delivered a variety of KPI's to different internal customers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Science Education Assistant} % Job title
    {Florida Polytechnic University} % Organization
    {Lakeland, Florida, USA} % Location
    {Sep. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Advanced Quantitative Methods QMB3200 tutor and grader.}
        \item {Mentored student with tasks in R and Stata; debugging regressions, data preparation, analysis interpretation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Science Intern} % Job title
    {Gulfstream Aerospace Corporation} % Organization
    {Savannah, Georgia, USA} % Location
    {May. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted in building investigative machine learning models which utilized over 50,000 unique aircraft sensors. The models were used to help debug malicious interactions in sensor busses.}
        \item {Developed pipelines to collect 100+ different macroeconomic variables to be used in sales forecasting. The process was entirely automated and validated data continuously.}
        \item {Kick started sales forecasting efforts using auto-regressive distributed lag models to predict quarterly sales. Models were cross validated with 90\%+ accuracy.}
        \item {Performed exploratory data analysis on different customers to define high value targets for the sales team. Finding were presented to both marketing and sales teams. The consequent quarter broke company sales records.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analyst} % Job title
    {Yes.Fit} % Organization
    {Lakeland, Florida, USA} % Location
    {Mar. 2018 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automated inventory reporting reducing labor hours for inventory planning by a factor of 2.}
        \item {Authored reports on customer behaviour and advertising effectiveness to guide leadership with optimizing advertising expenditure.}
        \item {Spearheaded an effort to build dashboards to deliver real-time analytics to the leadership teams.}
        \item {Forecasted inventory needs with over 95\% accuracy consistently for a variety of products and promotions.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
